---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whpt

The goal of `whpt` package is to predict WHPT scores, and assess them against
the expected class. This shows if a WHPT score is consistent with what is
expected at a given location.

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ecodata1/whpt")
```
### Example

To run the prediction and check the consistency:

```{r example, message=FALSE, warning=FALSE}

library(whpt)
library(dplyr)
whpts(demo_data)

```

### Predict

To run a prediction, only need "GIS" and date variables (but you can have extra
variables and doesn't matter what order or upper /lower case:)

```{r}
# Select only the variables needed to run a prediction:
data <- demo_data
names(data) <- tolower(names(data))
 data <- select(
    data,
    sample_id,
    date_taken,
    ngr,
    altitude,
    d_f_source,
    logaltbar,
    log_area,
    disch_cat,
    slope,
    chalk,
    clay,
    hardrock,
    limestone,
    peat)

whpt_predict(data)

```

### Predict and Assess

To run a prediction and then assess consistency:

```{r}

predictions <- whpt_predict(demo_data)
data <- bind_rows(demo_data, predictions)
consistency(data)

```


