---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whpt

The goal of `whpts` package is to predict whpt scores, and assess them against
the expected class. This shows if a whpt score is consistent with what is
expected at a given location.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ecodata1/whpt")
```
## Example

To run the prediction and check the consistency:

```{r example}

library(whpts)
whpts(demo_data)

```

To run only a prediction

```{r}
whpt_predict(demo_data)
```

To run a prediction and then assess consistency:

```{r}

predictions <- whpt_predict(demo_data)
data <- merge(demo_data, predictions,by.x =  "sample_id", by.y = "sample_id")
consistency(data)

```


